%-----------------------------------------
% Shen Huang
% Resume
%
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}

\moderncvtheme[darkred]{casual}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[utf8]{inputenc}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco} 

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR


% Personal Information 
\firstname{Shen}
\familyname{Huang}
\mobile{(303) 243-2881}
\email{Shen.Huang@Colorado.edu}
\homepage{alwa.info}
\extrainfo{https://github.com/LichAmnesia}

\title{Shen Huang's Resume}

% \nopagenumbers{}
\usepackage{lastpage}%获得总页数
\usepackage{fancyhdr}
\pagestyle{fancy}
% \rfoot{\thepage\ / \pageref{LastPage}}%当前页 of 总页数

\begin{document}

\maketitle
\section{Education}
\cventry{-Dec. 2017}{GPA: 3.9}{Master of Computer Science, University of Colorado Boulder}{}{}{} % Overall GPA: 3.949}{CSC \& MA Majors GPA: 4.0
\cventry{-Jul. 2016}{GPA: 3.9}{Bachelor of Computer Science, Nanjing University of Science \& Technology}{}{}{}{} % Overall GPA: 3.949}{CSC \& MA Majors GPA: 4.0
\section{Work Experience} 
  % Clean data by AP and WiFi 
  \cventry{Jun. 2017 -Aug. 2017}{Software Development Engineer Intern}{Amazon.com, Inc.}{Seattle, WA}{}{
      \begin{itemize}
        \item Built a recommendation system to provide advertisers better suggestions based on users' organic search.
        \item Developed a ML recommendation model in \textbf{Spark} to provide advertisers keywords to bid.
        \item Utilized \textbf{Solr} to index search results database as a solution to personal search.
        \item Deployed a \textbf{Pig} script to evaluate advertising performance and adjust recommendation model. 
      \end{itemize}
  }
  % \cventry{Sep. 2016 -May. 2017}{Research Assistant}{Advised by Prof. Brian C. Keegan}{University of Colorado Boulder}{}{
  %   \begin{itemize}
  %     \item Tried to solve a network science problem of denoising in a high dense graph.
  %     \item Used \textbf{DNN model} to learn the core structure in different kinds of graphs.
  %   \end{itemize}
  % } 

  % Clean data by AP and WiFi 
  \cventry{Jan. 2016 -May. 2016}{Data Science Engineer Intern}{Future Network Institute}{Nanjing, P.R. China}{}{
      \begin{itemize}
        \item Contributed to a national \textbf{software-defined networking} project to enable large-scale network control. 
        \item Developed a system for analyzing national network flow and data uploading APIs from network devices.
        \item Used \textbf{Hive} and \textbf{Hbase} to deal with the whole log data provided by routers. 
      \end{itemize}
  }
  
  % \cventry{Sep. 2015 -Jul. 2016}{Research Assistant}{Pattern Recognition and Bioinformatics Group in NJUST}{Nanjing, P.R. China}{}{
  %   \begin{itemize}
  %     \item Tried to solve a protein problem of predicting high-dimensional structure from protein sequence.
  %     \item The traditional strategy for this topic used machine learning methods. Implemented these and proposed a new feature extraction method, which used 3D information and annotated information.
  %     \item Tried to use \textbf{DNN model} in this problem and succeeded to get higher AUC in this problem. 
  %   \end{itemize}
  % } 
  % \cventry{Jan. 2015 -Jan. 2016}{Teaching Assistant}{C Programming Language for international students}{Nanjing, P.R. China}{}{
  %   \begin{itemize}
  %     \item Assisted professor to help students about problems in programming.
  %     \item Supervised students' practical team project work by giving advise on techniques.
  %   \end{itemize}
  % } 
\section{Student Projects} 
  \cventry{Feb. 2017 -May. 2017}{Yelp Restaurant Recommendation System}{}{}{}{
    \begin{itemize}
      \item Developed an algorithm on yelp dataset to recommend restaurants to users based on predicted preference.
      \item Used \textbf{Word2vec} in Gensim to get vector representation of restaurants and users.
      \item Built a \textbf{LSTM} and \textbf{softmax} model to classify restaurants for recommendation.
    \end{itemize}
  }
  % Event Create and Share
  \cventry{Sep. 2016 -Nov. 2016}{Event Create and Share Website}{}{}{}{
    \begin{itemize}
      \item Built a website that allow users to create events. People who are interested can participate in these events.
      \item Utilized \textbf{Spring MVC} and \textbf{myBatis} to build the backend and \textbf{Redis} to handle backend job queue.
      \item Developed Ajax based frontend services by \textbf{React} and \textbf{Redux}.  
      \item Followed \textbf{Material Design} pattern to design user interface, style, widgets and layout.
    \end{itemize}
  }
  \cventry{Aug. 2016 -Nov. 2016}{MusicFM online platform}{}{}{}{
    \begin{itemize}
      \item Built an online music platform using \textbf{Node.js} as backend and \textbf{Express} as frontend template.
      \item Developed a Python web scraper to scrape all music metadata (10 million songs) from an online music platform. Visualized all the data via \textbf{d3.js}.
      \item Performed ORM by \textbf{MongoDB}. Designed front-end UI by \textbf{Material Design} and \textbf{Angular}.
      \item Implemented a \textbf{Collaborative Filtering} algorithm to recommend top 5 songs for each user.
    \end{itemize}
  }
\section{Honors \& Awards}
\cventry{Mar. 2016}{Prize for Excellence in Asia Student Supercomputer Challenge}{Inspur Group Co., Ltd.}{}{}{}
\cventry{Oct. 2015}{Outstanding Students Award}{China Computer Federation}{}{}{}
\cventry{Jul. 2014}{Silver Medal in ACM/ICPC - Shanghai Inivation Contest}{ACM}{}{}{}
\section{Computer Skills}
  \cvline{Languages:}{Python, Java, JavaScript, SQL, R, Scala, C/C++, Mathematica}
  \cvline{Database:}{MySQL, MongoDb, Hbase, DynamoDB}
  \cvline{Environment:}{Hadoop, Spark, Pig, Hive, React, Angular, React Native}
% \section{Extra}
  % \cvlistitem{Contributor to open source projects - see \url{https://github.com/LichAmnesia}}
  % \cvlistitem{Core member of the Google Developer Groups Sub (Invited to Google I/O 2016)}
  % \cvlistitem{Help Huawei Technologies Co. set about 300 interview questions in their system}
\end{document}
