%-----------------------------------------
% Shen Huang
% Resume
%
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,letterpaper,final]{moderncv}
\usepackage{fontspec}

\moderncvtheme[darkred]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[utf8]{inputenc}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco} 

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR


% Personal Information 
\firstname{Shen}
\familyname{Huang}
\address{2156 Grove Cir W, Apt 2}{Boulder, CO 80302}
\mobile{(303) 243-2881}
\email{Shen.Huang@Colorado.edu}
\homepage{alwa.info}

\title{Shen Huang's Resume}

\nopagenumbers{}

\begin{document}

\maketitle

\section{Computer Skills} 
  \cvline{Languages:}{Python, C/C++, Ruby, JavaScript, Mathematica, Matlab}
\section{Experience} 
  % Bioinformatics 研究
  \cventry{September 2015 - July 2016}{Researcher in Machine Learning}{Pattern Recognition and Bioinformatics Group in NJUST}{Nanjing, China}{Supervised by Dongjun Yu}{
    \begin{itemize}
      \item Tried to solve a protein problem of predicting high-dimensional structural information via little information of protein sequence.
      \item The traditional strategy for this topic is using machine learning methods. Implemented these and propose a new feature extraction method.
      \item Tried to use DNN model in this problem and succeeded, which was not shown work in this field. 
    \end{itemize}
  }
  % RM 视觉比赛
  \cventry{April 2016 - June 2016}{Computer Vision Engineer}{NJUST}{Nanjing, China}{}{
    \begin{itemize}
      \item Participated in Robomasters Competition, which is a robot design and computer vision competition.
      \item Was in charge of designing unmanned vehicles with automatic target recognition, tracking system, and path planning function, which can automatically fire shells to fight against enemy unmanned vehicles.
      \item Used structural features to design a target tracking algorithm.
      \item Implemented Fast RCNN model for recoginizing the target in the video from the unmanned vehicles.
    \end{itemize}
  }
  % ASC 比赛
  \cventry{March 2016 -- April 2016}{Compete in ASC Student Supercomputer Challenge}{Inspur Group Co., Ltd.}{China}{}{
      \begin{itemize}
        \item Won Prize of Excellence in the challenge.
        \item Designed and optimize algorithms in HPC.
        \item Used HPCG Test to get highest possible efficiency.
        \item Gave an useful optimization for the DNN program on the CPU + MIC Platform.
      \end{itemize}
  }
  \cventry{January 2016 -- April 2016}{Data Science Engineering Intern}{Future Network institute}{Nanjing, China}{}{
      \begin{itemize}
        \item Aanlyzed the data provided by AP and WiFi monitors every day.
        \item Used Spark to deal with the whole log data provided by monitors. 
        \item Developed a model to track each person's network behavior in the whole system.
      \end{itemize}
  }
  \cventry{October 2015 - January 2016}{MusicFM website}{NJUST}{Nanjing, China}{}{
    \begin{itemize}
      \item Built an online music website (music.smilebooky.com) using node.js.
      \item Performed ORM and routing assignment using MongoDB as database.
      \item Designed front-end UI by using Bootstrap and Angular.
      \item Implemented a recommendation system by using clustering methods to recommend top 5 songs.
    \end{itemize}
  }

\section{Education}
\cventry{Fall 2016 - }{M.S, Computer Science,  University of Colorado Boulder}{Boulder, CO}{}{}{} % Overall GPA: 3.949}{CSC \& MA Majors GPA: 4.0
\cventry{Fall 2012 - Summer 2016}{Computer Science, Nanjing University of Science \& Technology}{Nanjing, China}{}{Overall GPA: 3.6}{CS Majors GPA: 3.6 Rank: 2} % Overall GPA: 3.949}{CSC \& MA Majors GPA: 4.0
\section{Extra}
  \cvlistitem{Contributor to open source projects - see \url{https://github.com/LichAmnesia}}
  \cvlistitem{5th Overall, Bronze Medal in the ACM - International Collegiate Programming Contest}
  \cvlistitem{3rd in the National Software Design Contest}
  \cvlistitem{Outstanding Students Award in China}
  \cvlistitem{Member of the GDG Sub}
\end{document}
